---
title: "Usage Vignette"
output: 
  html_document:
    keep_md: true
---

# Introduction

This vignette demonstrates the usage of the functions in the `redo.glm` package.

## Setup

```{r}
# install.packages("devtools")
# devtools::install_github("jennie-ui/redo.glm")
library(redo.glm)
```

## Demonstrate the usage of glmSetup

Consider a scenario where we have cell count ($Y$), and covariates: TNF (tumor necrosis factor) -- baseline variable, IFN (interferon) -- types of proteins in the body. We would like to quantify the relationship between TNF, IFN and cell count by different tests.

```{r}
# load data
Cell_Differentiation <- read.csv('data/Cell_Differentiation.csv')

# set up model parameters
glm_full <- glmSetup(res_var = "Count", base_var = "TNF", input_data = Cell_Differentiation, tolerance = 0.00001, log_offset = 0.1, max_iterations = 25)
```

The following variables are returned:

```{r}
# Histogram of the response variable
glm_full$histogram

# Log-transformed response variable
glm_full$transformed_response

# Model design matrix
glm_full$design_matrix

# Number of observations (n)
glm_full$n

# Number of coefficients (q, including beta_0)
glm_full$num_predictors
```

## Demonstrate the usage of glmPoisson

Estimate $\beta$ using IRWLS, and evaluate the Poisson regression model we proposed.

A list of variables will be returned:

```{r}
# Variance covariance matrix Var(beta_hat) for beta
glmPoisson(glm_full)$variance_covariance_matrix

# Estimates
glmPoisson(glm_full)$estimates

# standard deviation
glmPoisson(glm_full)$std

# confidence interval
glmPoisson(glm_full)$confidence_interval

# Pearson Residuals and Deviance Residuals
glmPoisson(glm_full)$residuals

# Leverage
glmPoisson(glm_full)$leverage

# Standardized Pearson and Deviance residuals
glmPoisson(glm_full)$standardized_residuals

# Cook's Distance
glmPoisson(glm_full)$cooks_distance

# Scaled deviance and Pearson chi-square statistics to assess the GoF of the model
glmPoisson(glm_full)$goodness_of_fit
```

## Demonstrate the usage of glmBinomial

Estimate $\beta$ using IRWLS, and evaluate the binomial regression model we proposed.

A list of variables will be returned:

```{r}
# Variance covariance matrix Var(beta_hat) for beta
glmBinomial(glm_full)$variance_covariance_matrix

# Estimates
glmBinomial(glm_full)$estimates

# standard deviation
glmBinomial(glm_full)$std

# confidence interval
glmBinomial(glm_full)$confidence_interval

# Pearson Residuals
glmBinomial(glm_full)$residuals

# Leverage
glmBinomial(glm_full)$leverage

# Standardized Pearson residuals
glmBinomial(glm_full)$standardized_residuals

# Cook's Distance
glmBinomial(glm_full)$cooks_distance

# Pearson chi-square statistics to assess the GoF of the model
glmBinomial(glm_full)$goodness_of_fit
```
